%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {DevOps Engineer} % Job title
    {POS uslugi} % Organisation
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      Migrating a project from LXC containers to own Kubernetes, resulting in improved scalability, reliability, and resource utilization
      \end{cvitems}
    }


%---------------------------------------------------------
%  \cventry
%    {Python Developer, Maintainer} % Job title
%    {} % Organisation
%    {} % Location
%    {} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        Develop telegram bot for reserving tables in restaurant, using only mongodb.
%      \end{cvitems}
%    }

%---------------------------------------------------------
  \cventry
    {System Developer(Python), product support specialist } % Job title
    {} % Organisation
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems}
        I was responsible for developing and maintaining a comprehensive IT support system that included a chatbot for communicating with clients,
        a PBX for handling incoming calls, integrations with a ticketing system. and bot for monitoring and controlling this system from job chat.
        This system provided efficient and effective support to internal and external clients,
        while ensuring high levels of customer satisfaction and reducing response times
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer(Python, C++), product support specialist} % Job title
    {} % Organisation
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        I have experience developing customized IT solutions for the restaurant industry,
        including a variety of products such as telegram bots for IT support, table reservations, and a loyalty program management system.
        These solutions were designed to streamline restaurant operations, enhance customer engagement, and improve overall business efficiency.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Support} % Job title
    {} % Organisation
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Deploying and maintenance popular products(MS Active Directory, IIS, MSSQL, MS Exchange, Postgresql, etc.)}
        \item {Writing and customizing small utilities using various programming languages}
        \item {Deploying and maintenance business-specific products(iiko, r-keeper, sh4)}
        \item {Integration client's systems with outsource-projects}
        \item {System and network administration(local networks, vpn for internal services, public wifi's)}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Fullstack developer(JS, Python), product support specialist}
    {\href{https://anzujewelry.com/}{Anzu Jewelry}}
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems}
        I developed and maintained a system for accounting production in a jewelry workshop.
        The system was built using various technologies including systemd, GitLab CI, docker-compose, and PostgreSQL.
        In order to integrate with a digital registration system for precious metals
        , I utilized asynchronous processing with Celery and MongoDB.
        The system was designed with flexibility in mind, allowing for easy customization and adaptation to the changing needs of the jewelry workshop.
        This enabled the system to support various production processes and workflows, while maintaining high levels of accuracy and efficiency.
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {System administrator} % Job title
    {Mallina LTD} % Organisation
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {System and network administration}
        \item {Resolving IT-like problems}
        \item {Support users}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
